Predicting the 2024 US Presidential Election: A Polling-Based Forecast

### 2024-11-04 paper/paper.qmd
Add appendix
Add appendix a
Update the text
Update the text about data, result, model and appendix.

---
title: "Predicting the 2024 US Presidential Election: A Polling-Based Forecast"
subtitle: "Utilizing Statistical Models to Assess Donald Trump's Support"
author: 
  - Tianrui Fu
  - Yiyue Deng
  - Jianing Li
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder). and [https://projects.fivethirtyeight.com/polls/president-general/2024/national/](https://projects.fivethirtyeight.com/polls/president-general/2024/national/)"
date: today
date-format: long
abstract: "This paper uses polling data to predict the outcome of the 2024 U.S. presidential election. By applying generalized linear regression and Bayesian models, we analyze the factors related to the polls, including polling organizations and the ratings associated with those organizations, on Donald Trump’s support rate. The research results indicate a significant relationship between the variables, with Donald Trump’s support rate showing an upward trend. Additionally, we further discuss the advantages and disadvantages of the two models, as well as potential methods for improvement."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

We use the statistical programming language @citeR, the templete from @citeRohan completed by following packages：tidyverse @tidyverse, dplyr @dplyr, rstanarm @rstanarm, arrow @arrow, modelr @modelr, modelsummary @modelsummary, ggplot2 @ggplot2, here @citehere, kableExtra @kableExtra and knitr @citeknitr to complete this analysis. Our data about the latest polling outcomes is from the website @fivethirtyeight2024. It has 52 variables and 15891 observations in this data set, including pollster, poll score, etc.
```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: tbl-dataset-example
#| tbl-cap: The example of chosen variable datset
#| echo: false
set.seed(123)
analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
example_dataset <- analysis_data[sample(1:nrow(analysis_data), 10), c("pollster", "pollscore", "numeric_grade", "transparency_score", "end_date", "pct")]
kable(example_dataset, col.names = c("pollster", "pollscore", "numeric_grade", "transparency_score", "end_date", "pct")) %>%
  kable_styling() %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(0, extra_css = "border-bottom: 2px solid black;")  
```

## Cleaning Data
We have cleaned the data set and the detailed procedure see from the appendix.

@@

After cleaning the data set, we have get about 38 variables and 492 observations about the polling outcomes for Donald Trump. In order to analysis if the different pollster can influence the final result of U.S. president election, we choose some related variable to build the Bayesian model. The related variables has the numeric grade, transparency score, poll score, pollster, the end date and percentage. The explain of each used variable please see in the @sec-cleandata.

@@

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-percentage-pollster
#| fig-cap: Percentage of Each Pollster Over Time
#| echo: false
ggplot(analysis_data, aes(x = end_date, y = pct, fill = pollster)) +
  geom_area(position = "stack", alpha = 0.7) +
  labs(x = "End Date", y = "Percentage (%)") +
  theme_minimal()
```

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-pct-density
#| fig-cap: Density plot of pct
#| echo: false
ggplot(analysis_data, aes(x = pct)) +
  geom_density(fill = "lightblue", color = "blue", alpha = 0.5) +
  labs(title = "Density Plot of Pct", x = "Pct", y = "Density") +
  theme_minimal()
```
## Predictor variables

@@

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-frequency-bar
#| fig-cap: Frequency of each pollster
#| echo: false
ggplot(analysis_data, aes(y = reorder(pollster, table(pollster)[pollster]))) +  
  geom_bar(aes(fill = after_stat(count)), color = "black") +                          
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.1, size = 2) +  
  scale_fill_gradient(low = "lightblue", high = "blue") +
  labs(x = "Count", y = "Pollster") +       
  theme_minimal() +
  theme(axis.text.x = element_text(size = 8)) 
```
In @fig-avg-pollscore, the predictor variable is the average poll score for each pollster over time, from August to October. This heat map visualizes the poll scores of each organization on different dates, with color intensity indicating the score levels—darker colors represent lower scores. The pollsters with the most consistently low average poll scores (darker colors) include Selzer, Siena/NYT, and Marquette Law School. These pollsters frequently show results lower than others over time, suggesting they may consistently lean toward one direction in their results. In contrast, pollsters like YouGov Center for Working Class Politics and YouGov Blue display lighter colors, indicating relatively higher scores across their polls.
```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-avg-pollscore
#| fig-cap: Average Pollscore by Pollster and End Date
#| echo: false
library(dplyr)

heatmap_data <- analysis_data %>%
  group_by(pollster, end_date) %>%
  summarise(mean_pollscore = mean(pollscore, na.rm = TRUE), .groups = "drop")

@@

```
In @fig-plot, there is a clear positive relationship between transparency score and numeric grade. Pollsters with higher transparency scores, such as those scoring around 10, tend to achieve higher numeric grades, close to 3.0. Conversely, pollsters with lower transparency scores tend to have lower numeric grades, closer to 2.7. This pattern suggests that greater transparency is associated with better overall pollster ratings.
```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-plot
#| fig-cap: Scatter Plot of transparency score and numeric grade
#| echo: false
#| message: false
#| warning: false
suppressWarnings({
  ggplot(analysis_data, aes(x = transparency_score, y = numeric_grade)) +
    geom_point(color = "darkblue", alpha = 0.6) +
    geom_smooth(method = "lm", color = "red", se = FALSE) +
    labs(x = "Transparency Score", y = "Numeric Grade") +
    theme_minimal()
})
```

@@

The goal of our modeling strategy is twofold. Firstly, we aim to estimate the impact of key factors—such as pollster reliability scores, transparency, and specific pollster effects—on polling results. Secondly, we seek to analyze how these effects change over time. Here, we briefly describe the Bayesian analysis model used to investigate these relationships.
Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up
In this Bayesian framework, we assume a normal distribution of poll results around a mean affected by key predictors: numeric grade, transparency score, and pollscore. Define $y_i$ as the percentage. Then $\beta_i$ represents the numeric grade, $\gamma_i$ represents the transparency score, and $\delta_i$ represents the pollscore.

\begin{align}
y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i + \beta_3 \cdot \text{pollscore}_i \\
&\quad + \sum_{j=1}^{N} \gamma_j \cdot \text{pollster}_j + \delta_i \cdot \text{end\_date}_i \\
\alpha &\sim \text{Normal}(50, 10) \\
\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 5) \\
\gamma_j &\sim \text{Normal}(0, 5) \\
\sigma &\sim \text{Exponential}(1)
\end{align}
where the intercept $\alpha$ represents an average poll result, and each $\beta$ coefficient captures the unique effect of its respective predictor on the poll percentage. The variable 
$ pollster_j $ denotes a specific pollster effect, while $ end date_i $ accounts for time trends. Priors are applied as follows: $\alpha$ follows a normal distribution centered at 50 with a standard deviation of 10, and each $\beta$ and $\gamma$ parameter is set to a normal prior of mean 0 and standard deviation 5, reflecting mild assumptions about effect direction without biasing their magnitude. Finally, the noise parameter $\sigma$ follows an exponential distribution with rate 1, allowing flexibility in unexplained variation. We run the model in @citeR using the package of @rstanarm.

### Model justification

This model balances complexity with interpretability, accounting for factors like numeric grades and transparency scores while maintaining computational simplicity. Predictors such as pollscore and transparency score were chosen based on their significance in the data section, reflecting reliability and potential biases. Including individual pollster effects as fixed coefficients captures potential pollster-specific deviations, while end date trends allow us to observe temporal shifts in poll support. This structure is intended to balance explanatory power with generalizability.

@@

Our results are summarized in @tbl-modelresults and the plot for glm and bayesian is in @fig-final and @fig-bayes respectively.

@@

model_final_glm <-
  readRDS(file = here::here("models/model_final.rds"))
model_bayes <-
  readRDS(file = here::here("models/model_bayes.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false
library(modelsummary)
library(kableExtra)
library(dplyr)
coef_names <- c("end_date" = "End Date",
                "pollsterBeacon/Shaw" = "Beacon/Shaw",
                "pollsterChristopher Newport U." = "Christopher Newport U.",
                "pollsterCNN/SSRS" = "CNN/SSRS",
                "pollsterData Orbital" = "Data Orbital",
                "pollsterEchelon Insights" = "Echelon Insights",
                "pollsterEmerson" = "Emerson",
                "pollsterIpsos" = "Ipsos",
                "pollsterMarist" = "Marist",
                "pollsterMarquette Law School" = "Marquette Law School",
                "pollsterMassINC Polling Group" = "MassINC Polling Group",
                "pollsterMcCourtney Institute/YouGov" = "McCourtney Institute/YouGov",
                "pollsterMuhlenberg" = "Muhlenberg",
                "pollsterQuinnipiac" = "Quinnipiac",
                "pollsterSelzer" = "Selzer",
                "pollsterSiena" = "Siena",
                "pollsterSiena/NYT" = "Siena/NYT",
                "pollsterSuffolk" = "Suffolk",
                "pollsterSurveyUSA" = "SurveyUSA",
                "pollsterSurveyUSA/High Point University" = "SurveyUSA/High Point University",
                "pollsterThe Washington Post" = "The Washington Post",
                "pollsterU. North Florida" = "U. North Florida",
                "pollsterUniversity of Massachusetts Lowell/YouGov" = "University of Massachusetts Lowell/YouGov",
                "pollsterWashington Post/George Mason University" = "Washington Post/George Mason University",
                "pollsterYouGov" = "YouGov",
                "pollsterYouGov Blue" = "YouGov Blue",
                "pollsterYouGov/Center for Working Class Politics" = "YouGov/Center for Working Class Politics")

modelsummary(models = list("Model by glm" = model_final_glm, 
                           "Model by bayes" = model_bayes),
             statistic = "conf.int",
             conf_level = 0.95,
             stars = TRUE,
             coef_rename = coef_names,
             output = "kableExtra") %>%
  kable_styling(full_width = F, position = "left", bootstrap_options = c("striped", "hover"
                                                                           , line_height = 6)) %>%
  column_spec(column = 2, width = "2em") %>%
  column_spec(column = 2, width = "4em") %>%
  add_header_above(c(" " = 1, "Model Summary" = 2)) %>%
  kable_classic(full_width = F, font_size = 4) %>%
  add_footnote("This table shows the regression models with custom variable names.")

@@

```{r}
#| echo: false
#| eval: true
#| label: fig-final
#| fig-cap: GLM with pollster, related variable and date
#| warning: false
#| message: false
library(modelsummary)
library(modelr)
analysis_data <- analysis_data |>
  add_predictions(model_final_glm, var = "final")

ggplot(analysis_data, aes(x = end_date)) +
  geom_point(aes(y = pct), color = "black") +
  geom_smooth(aes(y = final), color = "red", linetype = "dotted") +
  theme_classic() +
  labs(y = "Trump Percent", x = "Date")
```

```{r, fig.pos= 'H', fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-bayes
#| fig-cap: Poll Percentage over Time with Bayesian Fit
#| warning: false

new_data <- data.frame(
  end_date = seq(
    min(analysis_data$end_date),
    max(analysis_data$end_date),
    length.out = 100
  ),
  numeric_grade = mean(analysis_data$numeric_grade),
  pollscore = mean(analysis_data$pollscore),
  transparency_score = mean(analysis_data$transparency_score),
  pollster = factor("AtlasIntel")
)

posterior_preds <- posterior_predict(model_bayes, newdata = new_data)

ggplot(analysis_data, aes(x = end_date, y = pct, color = pollster)) +
  geom_point() +
  geom_line(
    data = pred_summary,
    aes(x = end_date, y = pred_mean),
    color = "blue",
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary,
    aes(x = end_date, ymin = pred_lower, ymax = pred_upper),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  labs(
    x = "End Date",
    y = "Percentage"
  ) +
  theme_minimal() +
  theme(
    legend.key.size = unit(1, "cm"),
    legend.text = element_text(size = 5) 
  )
```

>>>>

---
title: "Predicting the 2024 US Presidential Election: A Polling-Based Forecast"
subtitle: "Trump will get support about 47.55% by pollster and may lose the election"
author: 
  - Tianrui Fu
  - Yiyue Deng
  - Jianing Li
thanks: "Code and data are available at: [https://github.com/FrankFU323/U.S.-presidential-election.git](https://github.com/FrankFU323/U.S.-presidential-election.git)"
date: today
date-format: long
abstract: "This paper uses polling data to predict the outcome of the 2024 U.S. presidential election. By applying generalized linear regression and Bayesian models, we analyze the factors related to the polls, including polling organizations and the ratings associated with those organizations, on Donald Trump’s support rate. The research results indicate a significant relationship between the variables, with Donald Trump’s support rate showing an upward trend. Additionally, we further discuss the advantages and disadvantages of the two models, as well as potential methods for improvement."
format: pdf
header-includes:
   - \usepackage{amsmath}
toc: true
number-sections: true
bibliography: references.bib
---

@@

We use the statistical programming language @citeR, the templete from @citeRohan completed by following packages：tidyverse @tidyverse, dplyr @dplyr, rstanarm @rstanarm, arrow @arrow, modelr @modelr, modelsummary @modelsummary, ggplot2 @ggplot2, here @citehere, kableExtra @kableExtra and knitr @citeknitr to complete this analysis. Our data about the latest polling outcomes is from the website @fivethirtyeight2024. It has 52 variables and 15891 observations in this data set, including pollster, poll score, etc.

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: tbl-dataset-example
#| tbl-cap: The example of chosen variable datset
#| echo: false

set.seed(123)
analysis_trump <- read_parquet(here::here("data/02-analysis_data/analysis_data_trump.parquet"))
analysis_harris <- read_parquet(here::here("data/02-analysis_data/analysis_data_harris.parquet"))
example_dataset <- analysis_trump[sample(1:nrow(analysis_trump), 10), c("pollster", "pollscore", "numeric_grade", "transparency_score", "end_date", "pct")]
kable(example_dataset, col.names = c("pollster", "pollscore", "numeric_grade", "transparency_score", "end_date", "pct")) %>%
  kable_styling(full_width = F, position = "center") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(0, extra_css = "border-bottom: 2px solid black;")  
```

## Cleaning Data
We have cleaned the data set and the detailed procedure see from the appendix @sec-cleandata.

@@

In the realm of political polling, measurement is critical as it transforms abstract voter sentiments into quantifiable estimates that can influence electoral outcomes. The fundamental challenge lies in converting individual opinions—such as a voter's intention to support a particular candidate—into structured data that can effectively forecast the number of electoral college votes that candidate might secure. This transformation begins with the design of the polling methodology, where specific phenomena in the real world, such as voter preferences, are captured through surveys.

This dataset originates from @fivethirtyeight2024, a trusted source known for its rigorous standards in polling data collection, ensuring the widest possible coverage of voters and comprehensive collection and disclosure of all relevant information. This includes details like the pollster's name, identification number, survey dates, and associated trust levels. In our analysis dataset, which consists of 492 observations related to Donald Trump's polling outcomes, we have identified 38 relevant variables that play a significant role in understanding electoral support. Key among these are the numeric grade, transparency score, poll score, pollster, end date, and percentage of support for Trump. Each variable is meticulously measured to ensure that they accurately reflect the sentiments of likely voters.

The dataset presents results as the proportion of votes each candidate receives according to each pollster, with this approach adjusting over time to account for changes in voter sentiment, which can shift rapidly due to the approach of Election Day, candidate speeches, and other factors. By applying these measurement principles, we systematically convert nuanced public opinion into a structured dataset that not only captures voter intentions but also provides a reliable foundation for predictive modeling.

Ultimately, this rigorous measurement approach allows us to build a Bayesian model to assess how different pollsters might influence the final outcome of the U.S. presidential election, thus bridging the gap between individual voter opinions and electoral predictions.

The explain of each used variable please see in the @sec-variable.

@@

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-percentage-pollster
#| fig-cap: Percentage of Each Pollster Over Time
#| echo: false
ggplot(analysis_trump, aes(x = end_date, y = pct, fill = pollster)) +
  geom_area(position = "stack", alpha = 0.7) +
  labs(x = "End Date", y = "Percentage (%)") +
  theme_minimal()
```

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-pct-density
#| fig-cap: Density plot of pct
#| echo: false
ggplot(analysis_trump, aes(x = pct)) +
  geom_density(fill = "#87CEEB", color = "blue", alpha = 0.5) +
  labs(title = "Density Plot of Pct", x = "Pct", y = "Density") +
  theme_minimal()
```
## Predictor variables

### Pollster

@@

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-frequency-bar
#| fig-cap: Frequency of each pollster
#| echo: false
ggplot(analysis_trump, aes(y = reorder(pollster, table(pollster)[pollster]))) +  
  geom_bar(aes(fill = after_stat(count)), color = "black") +                          
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.1, size = 2) +  
  scale_fill_gradient(low = "lightblue", high = "blue") +
  labs(x = "Count", y = "Pollster") +       
  theme_minimal() +
  theme(axis.text.x = element_text(size = 8)) 
```
### Poll Score

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-pollscore
#| fig-cap: Distribution of Poll Score
#| echo: false
#| message: false
#| warning: false

ggplot(analysis_trump, aes(x = pollscore)) +
  geom_histogram(binwidth = 0.1, fill = "#87CEEB", color = "black") +
  labs(
    title = "Distribution of Poll Score",
    x = "Poll Score",
    y = "Count"
  ) +
  theme_minimal()
```
### Transparency Score

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-transparency
#| fig-cap: Distribution of Transparency Score
#| echo: false
#| message: false
#| warning: false

ggplot(analysis_trump, aes(x = transparency_score)) +
  geom_histogram(binwidth = 1, fill = "#87CEEB", color = "black") +
  labs(
    x = "Transparency Score",
    y = "Count"
  ) +
  theme_minimal()
```
### Numeric Grade

```{r}
#| label: fig-numeric
#| fig-cap: Density Plot of Numeric Grade
#| echo: false
#| message: false
#| warning: false
ggplot(analysis_trump, aes(x = numeric_grade)) +
  geom_density(fill = "#87CEEB", alpha = 0.4) +
  labs(
    x = "Numeric Grade",
    y = "Density"
  ) +
  theme_minimal()
```
### End date

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-enddate
#| fig-cap: Frequency of Records by End Date
#| echo: false
#| message: false
#| warning: false

ggplot(analysis_trump, aes(x = end_date)) +
  geom_bar(fill = "#87CEEB", color = "black") +
  labs(
    x = "End Date",
    y = "Count"
  ) +
  theme_minimal()
```

### Relationship between pollster, pollscore and end date

In @fig-avg-pollscore, the predictor variable is the average poll score for each pollster over time, from August to October. This heat map visualizes the poll scores of each organization on different dates, with color intensity indicating the score levels—darker colors represent lower scores. The pollsters with the most consistently low average poll scores (darker colors) include Selzer, Siena/NYT, and Marquette Law School. These pollsters frequently show results lower than others over time, suggesting they may consistently lean toward one direction in their results. In contrast, pollsters like YouGov Center for Working Class Politics and YouGov Blue display lighter colors, indicating relatively higher scores across their polls.

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-avg-pollscore
#| fig-cap: Average Pollscore by Pollster and End Date
#| echo: false
library(dplyr)

heatmap_data <- analysis_trump %>%
  group_by(pollster, end_date) %>%
  summarise(mean_pollscore = mean(pollscore, na.rm = TRUE), .groups = "drop")

@@

### Relationship between transparency score and numeric grade

In @fig-plot, there is a clear positive relationship between transparency score and numeric grade. Pollsters with higher transparency scores, such as those scoring around 10, tend to achieve higher numeric grades, close to 3.0. Conversely, pollsters with lower transparency scores tend to have lower numeric grades, closer to 2.7. This pattern suggests that greater transparency is associated with better overall pollster ratings.

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-plot
#| fig-cap: Scatter Plot of transparency score and numeric grade
#| echo: false
#| message: false
#| warning: false
ggplot(analysis_trump, aes(x = transparency_score, y = numeric_grade)) +
  geom_point(color = "darkblue", alpha = 0.6) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(x = "Transparency Score", y = "Numeric Grade") +
  theme_minimal()
```

@@

## Model Selection

Our model aims to predict the changes in Donald Trump’s probability of winning the 2024 U.S. election over time while examining the influence of key factors, such as pollster reliability scores, transparency, and specific pollster effects, on polling results. For model selection, we initially considered a generalized linear regression to provide a straightforward analysis of the relationships between these factors. However, given the limitations of generalized linear regression in handling uncertainty and dynamic data, we ultimately chose a Bayesian model. The Bayesian approach enables the integration of prior information and dynamically updates predictions, offering greater stability and accuracy under high uncertainty. Below is a brief overview of our model.

Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up
In this Bayesian framework, we assume a normal distribution of poll results around a mean affected by key predictors: numeric grade, transparency score, and pollscore. Define $y_i$ as the percentage of Donald Trump. Then $\beta_i$ represents the numeric grade, $\gamma_i$ represents the transparency score, and $\delta_i$ represents the pollscore.

### Model 1 -- GLM

\begin{align} 
y_i &= \alpha + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i + \beta_3 \cdot \text{pollscore}_i \\
&\quad + \sum_{j=1}^{N} \gamma_j \cdot \text{pollster}_j + \delta \cdot \text{end\_date}_i + \epsilon_i 
\end{align}

where: 
- $\alpha$ is the intercept, representing the average poll level.
- $\beta_1$, $\beta_2$, and $\beta_3$ are the regression coefficients for numeric grade, transparency score, and pollscore, respectively.
- $\gamma_j$ indicates the fixed effect of each pollster.
- $\delta$ is the regression coefficient for the end date.
- $\epsilon_i$ is the error term.

### Model 2 -- Bayesian model for Trump

\begin{align}
y_i | \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i + \beta_3 \cdot \text{pollscore}_i \\
&\quad + \sum_{j=1}^{N} \gamma_j \cdot \text{pollster}_j + \delta_i \cdot \text{end\_date}_i \\
\alpha &\sim \text{Normal}(50, 10) \\
\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 5) \\
\gamma_j &\sim \text{Normal}(0, 5) \\
\sigma &\sim \text{Exponential}(1)
\end{align}

where:
- $\alpha$ represents an average poll result.
- $\beta_1$, $\beta_2$, and $\beta_3$ capture the unique effect of their respective predictors on the poll percentage.
- $\gamma_j$ denotes a specific pollster effect.
- $\delta_i$ accounts for time trends.

We run the model in @citeR using the package of rstanarm @rstanarm.

## Model justification

The choice of a Bayesian model to analyze Donald Trump’s voting support rate stems from the need to effectively integrate uncertainty and leverage prior knowledge in estimating outcomes. Given that the dataset includes key predictors related to polling organizations—such as numeric_grade, transparency_score, pollster, poll_score, end_date, and pct—this approach allows for a comprehensive understanding of how these variables influence voting results.

The numeric_grade and transparency_score are crucial in assessing the reliability of polling organizations. By integrating these factors, the Bayesian model can provide a nuanced analysis of how the quality and transparency of polling organizations impact Trump’s support rate. This is particularly important in the context of public opinion polling, as perceptions of reliability can significantly affect the interpretation of results.

Moreover, the Bayesian framework enables the incorporation of prior distributions for model parameters, reflecting beliefs about their possible values before observing the data. This is especially beneficial in a domain where historical data and expert opinion can provide valuable insights.

Additionally, by including the pollster variable, the model accounts for the fixed effects of different polling organizations, allowing for a more targeted analysis that acknowledges the unique characteristics of each organization. The end_date variable helps to consider time trends, ensuring that the analysis remains relevant to the evolving political landscape, especially as elections approach.

However, there are areas for improvement within the model. First, refining the selection of variables related to voting support could enhance the model’s predictive power. For instance, incorporating socio-economic factors, demographic data, or shifts in voter behavior may provide a more comprehensive perspective. Additionally, the model's predictive performance could be assessed through cross-validation or other model evaluation techniques to ensure the robustness and reliability of the results.

By employing this Bayesian model, our aim is to provide robust estimates of Trump’s support rate, considering both the statistical characteristics of the data and the inherent uncertainty related to polling, while exploring avenues for further model improvement.

@@

The results part is combined with the result for models of analysis data and the result of predictions by Bayesian model on November 5, 2024. In order to get to know whether the votes of Trump will win the election, we combined the data of Harris who have the most competitive candidate other than Trump to do predictions. It would help us be faster and more accurate to do the predict judgment.

## Result of model for analysis data

In @fig-final, we applied a generalized linear regression model to predict the percentage of polls Trump according each pollster. Specifically, the support rate data points range from 40% to 55%, with most clustered between 45% and 50%. The orange trend line shows a subtle upward trend, indicating a gradual increase in Trump's average support rate over time. For example, in early August, the support rate is around 45%, while by mid-October, the average support rate shown by the trend line is close to 50%. This suggests that Trump's support rate has risen by about 5% over these three months. For the model summary of Generalized Linear Regression and Bayesian Model, the table can see at @sec-model_result.

@@

model_final_glm <-
  readRDS(file = here::here("models/model_final.rds"))
model_bayes_trump <-
  readRDS(file = here::here("models/model_bayes_trump.rds"))
model_bayes_harris <-
  readRDS(file = here::here("models/model_bayes_harris.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: fig-final
#| fig-cap: Donald Trump Support Over Time by Generalized Linear Regression
#| warning: false
#| message: false
library(ggplot2)
library(modelsummary)
library(modelr)
analysis_trump <- analysis_trump |>
  add_predictions(model_final_glm, var = "final")

ggplot(analysis_trump, aes(x = end_date)) +
  geom_point(aes(y = pct), color = "#87CEEB", size = 2, alpha = 0.7) +
  geom_smooth(aes(y = final), color = "#D55E00", size = 1.2, se = FALSE) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
  theme_classic() +
  labs(y = "Trump Percent", x = "Date") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1))
```
In @fig-bayes-trump, we applied a bayesian model to predict the percentage of polls Trump according each pollster. Each data point is color-coded by pollster, with support rates ranging from 40% to 55%. The shaded gray area around the trend line represents the confidence interval, indicating the uncertainty in support rate variations. The overall trend line (blue) shows a slight upward trend, increasing from about 45% in August to nearly 50% in October. In particular, data points in early August are more dispersed, with some pollsters reporting low support rates (around 40%) and others reporting higher rates (over 50%). By October, most poll results have converged, with support rates centered between 45% and 50%. Notably, certain pollsters, like YouGov and Marist, provide either consistently higher or lower support rate estimates compared to others, indicating some bias or variation among polling organizations.

We also applied a Bayesian model to predict the percentage of polls Harris according each pollster. The figure can see it in @sec-model_result.

```{r, fig.pos= 'H', fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-bayes-trump
#| fig-cap: Poll Percentage over Time with Bayesian Fit for Trump
#| warning: false

new_data <- data.frame(
  end_date = seq(
    min(analysis_trump$end_date),
    max(analysis_trump$end_date),
    length.out = 100
  ),
  numeric_grade = mean(analysis_trump$numeric_grade),
  pollscore = mean(analysis_trump$pollscore),
  transparency_score = mean(analysis_trump$transparency_score),
  pollster = factor("AtlasIntel")
)

posterior_preds <- posterior_predict(model_bayes_trump, newdata = new_data)

ggplot(analysis_trump, aes(x = end_date, y = pct, color = pollster)) +
  geom_point() +
  geom_line(
    data = pred_summary,
    aes(x = end_date, y = pred_mean),
    color = "blue",
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary,
    aes(x = end_date, ymin = pred_lower, ymax = pred_upper),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  labs(
    x = "End Date",
    y = "Percentage"
  ) +
  theme_minimal() +
  theme(
    legend.key.size = unit(1, "cm"),
    legend.text = element_text(size = 5) 
  )

```
## Result for model prediction

@fig-pred-mean compares the predicted mean support rates for Trump and Harris across different polling organizations in 5th November of 2024. The vertical axis shows the predicted support rate (in percentage), and the horizontal axis lists the various pollsters. The red line represents Harris's predicted support rate, while the blue line represents Trump's.

For example, in predictions from Christopher Newport U. and MassINC Polling Group, Harris has a noticeably higher average support rate than Trump, exceeding 50%, while Trump's support rate is below 50%. In Siena's predictions, Trump’s support rate is slightly lower than Harris’s, reaching around 41%, while Harris’s support is close to 53%. In Christopher Newport U.'s, MassINC Polling Group's, Siena's and Washington Post/George Mason University's predictions, Trump's support rate is all lower than Harris's and have a big gap.

```{r, fig.pos= 'H', fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-pred-mean
#| fig-cap: Predicted Mean Percentage by Pollster for Trump and Harris
#| warning: false
# 获取所有的 pollsters 列表
all_pollsters_trump <- unique(analysis_trump$pollster)
all_pollsters_harris <- unique(analysis_harris$pollster)

# 定义一个空的数据框，用于存储结果
all_predictions <- data.frame()

# 循环遍历 Trump 的 pollsters
for (pollster in all_pollsters_trump) {
  new_data_trump <- data.frame(
    end_date = as.Date("2024-11-05"),
    numeric_grade = mean(analysis_trump$numeric_grade, na.rm = TRUE),
    pollscore = mean(analysis_trump$pollscore, na.rm = TRUE),
    transparency_score = mean(analysis_trump$transparency_score, na.rm = TRUE),
    pollster = factor(pollster) 
  )

  posterior_preds_trump <- posterior_predict(model_bayes_trump, newdata = new_data_trump)

  final_prediction_trump <- data.frame(
    pollster = pollster, 
    candidate = "Trump",
    pred_mean = mean(posterior_preds_trump),
    pred_lower = quantile(posterior_preds_trump, probs = 0.025),
    pred_upper = quantile(posterior_preds_trump, probs = 0.975)
  )

  all_predictions <- rbind(all_predictions, final_prediction_trump)
}

# 循环遍历 Harris 的 pollsters
for (pollster in all_pollsters_harris) {
  new_data_harris <- data.frame(
    end_date = as.Date("2024-11-05"),
    numeric_grade = mean(analysis_harris$numeric_grade, na.rm = TRUE),
    pollscore = mean(analysis_harris$pollscore, na.rm = TRUE),
    transparency_score = mean(analysis_harris$transparency_score, na.rm = TRUE),
    pollster = factor(pollster) 
  )

  posterior_preds_harris <- posterior_predict(model_bayes_harris, newdata = new_data_harris)

  final_prediction_harris <- data.frame(
    pollster = pollster, 
    candidate = "Harris",
    pred_mean = mean(posterior_preds_harris),
    pred_lower = quantile(posterior_preds_harris, probs = 0.025),
    pred_upper = quantile(posterior_preds_harris, probs = 0.975)
  )

  all_predictions <- rbind(all_predictions, final_prediction_harris)
}

ggplot(all_predictions, aes(x = pollster, y = pred_mean, color = candidate, group = candidate)) +
  geom_line(linewidth = 1.2) +
  geom_point() +  
  labs(
    x = "Pollster",
    y = "Predicted Mean (%)",
    color = "Candidate"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

@@

In @tbl-pred-wide, we merged and compared the Bayesian model predictions of the vote shares for Trump and Harris on November 5, 2024, by pollster. The green background color represents the same pollster, indicating that the side with the larger predicted vote share is expected to win based on the data collected and summarized by that pollster. Conversely, red indicates the losing side. In @tbl-pred-wide, a total of 27 pollsters participated in the polling, with 11 pollsters predicting a Trump victory and 16 pollsters predicting a Harris victory. In @tbl-pred-summary, we calculated the mean support for Trump and Harris, estimating Trump's probability of winning to be 41%. For the further more predictions about the Bayesian model, we can see at @sec-model_result.

```{r, fig.pos= 'H', fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: tbl-pred-wide
#| tbl-cap: Predictions for both Trump and Harris by pollster
#| warning: false
library(dplyr)
library(kableExtra)
# 将 Trump 和 Harris 的预测结果按 pollster 合并
predictions_wide <- reshape(all_predictions, idvar = "pollster", timevar = "candidate", direction = "wide")

# 计算每个 pollster 认为谁的支持率更高
predictions_wide <- predictions_wide |>
  mutate(
    winner = ifelse(pred_mean.Trump > pred_mean.Harris, "Trump", "Harris"),
    prob_trump_lead = ifelse(pred_mean.Trump > pred_mean.Harris, 1, 0)
  )
